Inferring Galactic Parameters from Chemical Abundances with Simulation-Based Inference

### 2025-02-26 src/tex/ms.tex
[showyourwork] overleaf sync

However, currently our NPE network is not particularly good at estimating ages from abundances alone. On average our inference for ages results in an APE of $\sim27\%$ which is slightly larger than the observational noise of $20\%$ that we add during the mock up of our data but well in agreement with current uncertainties of stellar age inference.

>>>>

However, currently our NPE network is not particularly good at estimating ages from abundances alone. On average our inference for ages results in an APE of $\sim21\%$ which is slightly larger than the observational noise of $20\%$ that we add during the mock up of our data but well in agreement with current uncertainties of stellar age inference that range from 15\% to 30\% for turn-off stars and giants respectively.
